{\it Proposal:}\\ Ultrashort pulsed microwave viral envelope disruption as a COVID-19 treatment

### 2020-10-22 documents/charge.tex
:((((((((((((
Gelgreen

@@

>>>>

look into the Gibbs–Donnan effect

@@

it would be interesting to compare the potential energy of assembling such a structure to the known host metabolic burden of assembling a virus.

%https://www.macmillanlearning.com/studentresources/college/physics/tiplermodernphysics6e/classial_concept_review/chapter_11_ccr_20_electrostatic_energy_of_a_sphere_of_charge.pdf

$U = 3/5 * 1/4 pi epsilon_0 Q^2 / R \approx 2.3e-7 $
%U = (3/5) * 1/(4*pi*electricConstant) *((1e7 electricCharge)^2 / 60 nanometers) = 2.30708e-7 J

The total is $6 \times 10^11$ ATP-equivalent.

%50 kJ per mole, 6.022*10^23 = 9.9634673e-13 * 50 kj = 5e-8 J

of course, much of the potential energy may have already existed in the host cell, so this is probably an invalid comparison. And if most of the charge is contributed by osmotic, ion , this potential energy may not be counted.

todo: is it possible for the charged core to compensate for the potential energy of the charged shell?
